Low Complexity Adaptive Beamformer\\ for Active Sonar Imaging

### 2015-08-14 LCAforActiveSonarImaging/lca.tex
la2pdf commit - 2015:08:14	23:48:15	(Fri14.Aug)

A beamformer is a spatial filter we apply to backscattered wavefield data to estimate the scatter strength from a particular point or direction. A coarse adjustment is first obtained by applying delays to the sensor channels to negate the difference in travel time from the point of interest, thereby aligning the phase of the signals coming from that source. Next a set of weights, or window, is applied to the sensors to Finally a set of weights  , which in effect achieve this by applying delays and weigths to the sensor channels to coherently combine signals from the direction of interest.

>>>>

A beamformer is a spatial filter we apply to backscattered wavefield data to perform e.g. source localization and amplitude estimation. In sonar image reconstruction we desire

 A coarse adjustment is usually achieved by applying delays to the sensor channels to negate the difference in travel time from the point of interest, and cause the  thereby aligning the phase of the signals coming from that source. Next a set of weights, or window, is applied to the sensors to Finally a set of weights  , which in effect achieve this by applying delays and weigths to the sensor channels to coherently combine signals from the direction of interest.
